### 2015-05-14 background.tex
cutting space in bg

Modern operating systems address the demand for responsiveness and performance by providing multiple sources of concurrency~\cite{corbet2005linux}: a kernel can invoke an arbitrary number of entry points from the same driver concurrently; a running driver process can block and be replaced by another process in the same driver; hardware interrupts can be handled concurrently; delayed code execution is the norm; and the user can insert or remove hardware components without rebooting the kernel (known as hot-plugging). All these possibilities can easily lead to \emph{data races}, which can be defined as follows:

>>>>

Modern operating systems address the demand for responsiveness and performance by providing multiple sources of concurrency~\cite{corbet2005linux}, such as: a kernel can invoke an arbitrary number of entry points from the same driver concurrently; a running driver process can block and be replaced by another process in the same driver; and hardware interrupts can be handled concurrently. All these possibilities can easily lead to \emph{data races}, which can be defined as follows:

### 2015-05-14 whoop.tex
cutting space in bg

We engineered the Chauffeur and \whoop components of our toolchain (denoted with grey boxes in Figure~\ref{fig:whoop}).  For the remaining components, we were able to re-use industrial-strength tools that are robust and battle-proven via their use in many complex software projects.

>>>>

We engineered the Chauffeur and \whoop components of our toolchain (denoted with grey boxes in Figure~\ref{fig:whoop}).  For the remaining components, we were able to reuse industrial-strength tools that are robust and battle-proven via their use in many complex software projects.
